Environmental stress drives intermediate plant and pollinator specialisation

### 2020-04-14 paper/manuscript.Rmd
Move sensitivity analysis results to the methods

We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental stress estimations. 
For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the bioclimatic suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.

@@

After performing our sensitivity analysis, we found that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress. 
This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
<!-- When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)). -->

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
loadd(sensitivity_species_name)
fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental stress error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks.", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "* ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")

>>>>

We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental stress estimations. 
For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the bioclimatic suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF. 
This analysis indicated that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress. 
This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
loadd(sensitivity_species_name)
fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental stress error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks. ", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "*, ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")

@@
